---
title: "Assessment1.3"
author: "Yash Mhaske S4614167"
date: "29/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# 1
# Data viz and wrangling


# 2

```{r, echo=TRUE}
library(tidyverse)
library(ggplot2)
library(skimr)

fastfood <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

head(fastfood)

skim(fastfood)


```
##The three variables Restaurant, salad and item are categorical variables. So these three are eligible for turning into a factor variable. However,the salad variable has only one category that is 'other'. So even if we skip that variable it wont make any difference.The x1 variable is a serial variable and therefore summary statistics of x1 is not of any use and needs to be converted into a factor.



# 3

```{r, echo=TRUE}

fastfood$X1 <- factor(fastfood$X1)
fastfood$restaurant <- factor(fastfood$restaurant)
fastfood$item <- factor(fastfood$item)
fastfood$salad <- factor(fastfood$salad)
skim(fastfood)



```

# 4


```{r, echo=TRUE}

 fastfood[is.na(fastfood)] <- 0



```

# 5

```{r, echo=TRUE}
fastfood$calories_type <- cut_interval(fastfood$calories,
                                       n=3,
                                labels=c("low", "med","high"),
                              levels = c("low", "med","high"),
                              ordered = TRUE
                                )

```

# 6

```{r, echo=TRUE}

ggplot(fastfood, aes(x=calories_type, fill= calories_type))+
         geom_bar( )+scale_fill_manual(values = c("chartreuse4","blue","red"))+
         theme(legend.position = "none")+
                     facet_wrap(~restaurant,ncol=4)

```
# 7


```{r, echo=TRUE}

trans_fat_percent <- round((fastfood$trans_fat/fastfood$total_fat)*100, 1)

fastfood$trans_fat_percent <- trans_fat_percent


```

# 8

```{r, echo=TRUE}
install.packages("extrafont")
#library(viridis)
#library(hrbrthemes)
#library(extrafont)
#font_import()
#loadfonts(device="win")
```


```{r, echo=TRUE}
  fastfood %>%
  
  ggplot( aes(x=trans_fat_percent, color=restaurant, fill=restaurant)) +
    geom_histogram(alpha=0.6, binwidth = .5) +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    ) +
    xlab("trans fat (%)") +
    ylab("count") +
    facet_wrap(~restaurant)
```

# 9

``` {r, echo=TRUE}

fastfood %>% group_by(restaurant) %>% summarize(
  `mean total fat` = round(mean(total_fat),1))


```
# 11

``` {r, echo=TRUE}

viz <- fastfood %>% group_by(restaurant) %>% summarize(
  `mean total fat` = round(mean(total_fat),1))
library(RColorBrewer)
coul <- brewer.pal(8, "Set2") 
barplot(height=viz$`mean total fat`, names=viz$restaurant, col=coul, xlab="Restaurant", ylab="Mean total fat",
        ylim = c(0,40), main="Bar chart of mean total fat per restaurant")



```