---
title: "Assesment 1.1"
author: "Yash Mhaske s4614167"
date: "14/05/2021"
output: html_document
---
# RMarkDown Editing
*This is a Rmarkdown document.* 
*Markdown is a simple formatting syntax for authoring HTML,PDF, and MS Word Documents. For more details on using RMarkdown see* 
[https://rmarkdown.rstudio.com/lesson-8.html]
*The documentation on the website is really helpful and covers each and every aspect a new coder programming in R needs.*


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installing packages and assigning variable
```{r}
#install.packages("tidyverse")
library(tidyverse)
fastfood<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

## Displaying the first 10 records of the data set
```{r}
fastfood%>%head(10)
```

## Cleaning names with the help of the library janitor
```{r}
#install.packages("janitor")
library(janitor)
fastfood<-fastfood%>%
  clean_names()

fastfood%>%glimpse()
```

## Food with more than 1000 calories
```{r}
fastfood%>%filter(calories>1000)
```

## Food with Total fat more than 40 and Total carb more than 80 
```{r}
dont_eat_this<-fastfood%>%
  filter(total_fat>=40 & total_carb>=80)
dont_eat_this
```


